---
title: "Primary_Rating_Analysis"
author: "Niklas"
date: "2024-10-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(dev = "png" ,echo = TRUE)
```

## Primary Rating Analysis

Here I will describe and evaluate our measurement of rating specific touch actions. 

This document will have 3 segments:  

-Descriptive Statistics  

-Validity Check (Through (Sediment) and Frequency)  

-Explorativ (Role, Specific Touch)

```{r, include=FALSE, warning=FALSE}
library(ggplot2)
library(dplyr)
library(knitr)
library(stringr)
library(wordcloud)

set.seed(72)
##Set base directory with input files
#setwd(dirname(rstudioapi::getActiveDocumentContext()$path))

load("ReduceddataTokens.RData")

#remove irrelevant data frames from global environment
rm(list = setdiff(ls(), "reduceddata"))

#change the variables classes (numeric, vector)
reduceddata$rating <- as.numeric(reduceddata$rating)


#turn frequency into a factor
levels_freq <- c("Nie", 
                 "Seltener als 1 Mal pro Jahr", 
                 "1-5 Mal pro Jahr", 
                 "1 Mal pro Monat", 
                 "1 Mal pro Woche", 
                 "2-3 Mal pro Woche", 
                 "Täglich")

reduceddata$frequency3 <- factor(reduceddata$frequency, levels = levels_freq , labels = levels_freq)

#Replace NA values in 'frequency3' column with "Taeglich" to fix a bug

levels(reduceddata$frequency3)[7] <- "Taeglich"

reduceddata$frequency3[is.na(reduceddata$frequency3)] <- "Taeglich"

#Only look at rating and frequency for each touch once
reduceddata$rating_1 <- ifelse(reduceddata$NumberAdjective == "1",reduceddata$rating, NA)

reduceddata$freq_1 <- ifelse(reduceddata$NumberAdjective == "1", reduceddata$frequency3, NA)

reduceddata$freq_1 <- factor(reduceddata$freq_1, levels = c("1", "2", "3", "4", "5", "6", "7"), labels = c("Nie", 
                 "Seltener als 1 Mal pro Jahr", 
                 "1-5 Mal pro Jahr", 
                 "1 Mal pro Monat", 
                 "1 Mal pro Woche", 
                 "2-3 Mal pro Woche", 
                 "Taeglich"))

reduceddata$Role <- factor(reduceddata$Role, levels = c("active", "passive"), labels = c("active", "passive"))

reduceddata$rating <- as.numeric(reduceddata$rating)

#Split Action into Role and Bodypart
split_data <- do.call(rbind, strsplit(reduceddata$Action, "\\."))
reduceddata$ActionOnly <- split_data[, 1]
reduceddata$Bodypart <- split_data[, 2]

#Correct Typos
reduceddata$Bodypart<- str_replace(reduceddata$Bodypart, "UpperBac" , "UpperBack")
reduceddata$Bodypart<- str_replace(reduceddata$Bodypart, "UpperBackk" , "UpperBack")
reduceddata$Bodypart<- str_replace(reduceddata$Bodypart, "Cheek" , "Cheeks")
reduceddata$Bodypart<- str_replace(reduceddata$Bodypart, "Cheekss" , "Cheeks")


```
  
    
# Summary of Variable and Histogram

Here is an overview over the variable "Rating" and its distribution. 

```{r, echo = FALSE, warning=FALSE}
summary(reduceddata$rating_1)

ggplot(reduceddata, aes(x = rating_1)) +
  geom_histogram(binwidth = 0.5) +
  labs(x = "Rating Scores", Y = "Count")

```

## Validity Check 
In this section, I want to investigate how well rating actually is related to other concept, to prove its convergent validity. 

1. Frequency
How is the rating related to Frequency.

```{r, warning=FALSE}

plot(reduceddata$freq_1, col = "lightblue")

ggplot(reduceddata, aes(x = freq_1, y = rating_1)) +
  geom_violin(na.rm = TRUE, fill = "lightblue") +
  labs(title = "Ratings by Frequency Category", 
       x = "Frequency Category", 
       y = "Rating") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 

ggplot(reduceddata, aes(x = freq_1, y = rating_1, fill = Role)) +
  geom_violin(na.rm = TRUE, position = position_dodge(0.8)) +
  labs(title = "Ratings by Frequency Category and Role", 
       x = "Frequency Category", 
       y = "Rating") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_manual(values = c("lightblue", "lightcoral"))

paste("Spearman Correlation of", round(cor(reduceddata$rating_1, as.numeric(reduceddata$freq_1), method = "spearman", use = "complete.obs"), 2), "between Rating and Frequency")

```

The measurement of rating seems valid, as there is a strong relation between Frequency and Rating, as people engage more in touches that are pleasant. A further analysis on rating and sediment could be helpful to verify the validity of rating. A follow-up on this is at the end with word clouds, presenting the "high rated" Adjectives.

# Investigating research relevant variables

In this section, I try to visualize the relationship between the Rating and the variables relevant to our research question (like Role or Specific Touch)

## Rating across Roles
```{r}
ggplot(reduceddata, aes(x = Role, y = rating_1)) +
  geom_boxplot(na.rm = TRUE)

# Calculate descriptive statistics for rating_1 by Role
descriptives <- reduceddata %>%
  group_by(Role) %>%
  summarise(
    Mean = mean(rating_1, na.rm = TRUE),
    Median = median(rating_1, na.rm = TRUE),
    SD = sd(rating_1, na.rm = TRUE),
    IQR = IQR(rating_1, na.rm = TRUE),
    Q1 = quantile(rating_1, 0.25, na.rm = TRUE),
    Q3 = quantile(rating_1, 0.75, na.rm = TRUE),
    Count = n()
  )

kable(descriptives, caption = "Rating Scores in the different Roles")

##Wilcox Test 
wilcox.test(rating_1 ~ Role, data = reduceddata)

```

## Rating across touch situations (Bodypart and Action)

```{r, echo = FALSE, warning=FALSE}
ggplot(reduceddata, aes(x = Action, y = rating_1)) +
  geom_boxplot(na.rm = TRUE, fill = "lightblue", color = "black") +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +  
  labs(title = "Distribution of Ratings Across Actions", x = "Action", y = "Rating")

ggplot(reduceddata, aes(x = Bodypart, y = rating_1)) +
  geom_violin(na.rm = TRUE, fill = "lightyellow", color = "black") +
  stat_summary(fun = "mean", geom = "point", color = "darkblue", size = 3) +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +  
  labs(title = "Distribution of Ratings Across Bodyparts", x = "Bodypart", y = "Rating")

ggplot(reduceddata, aes(x = ActionOnly, y = rating_1)) +
  geom_violin(na.rm = TRUE, fill = "lightgreen", color = "black") +
  stat_summary(fun = "mean", geom = "point", color = "darkblue", size = 3) + 
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +  
  labs(title = "Distribution of Ratings Across ActionOnly", x = "Action", y = "Rating")


```


## Add-On: Wordclouds based on Rating

To support the validity of the Rating I created 4 Word-Clouds. One for all touches. And then 3 for touches grouped by low, mid and high rating. 

```{r, echo=TRUE, warning=FALSE}
##Create a Word Cloud 
general_adj <- (reduceddata$Adjective)

# Subset adjectives for each rating zone
low_ratings_adj <- reduceddata$Adjective[reduceddata$rating >= -100 & reduceddata$rating_1 <= 20]
mid_ratings_adj <- reduceddata$Adjective[reduceddata$rating > 20 & reduceddata$rating_1 <= 80]
high_ratings_adj <- reduceddata$Adjective[reduceddata$rating > 80 & reduceddata$rating_1 <= 100]
```

## All Ratings 

```{r, echo=FALSE, warning=FALSE}

wordcloud(words = general_adj, 
         min.freq = 8,  # Minimum frequency of words
         scale = c(3, 1),  # Size range for words
         colors = brewer.pal(8, "Dark2")) 
```

## Low Ratings

```{r, echo=FALSE, warning=FALSE}
wordcloud(words = low_ratings_adj, 
         min.freq = 5,  # Minimum frequency of words
         scale = c(3, 1),  # Size range for words
         colors = brewer.pal(8, "Blues"))
```

## Mid Ratings

```{r, echo=FALSE, warning=FALSE}
wordcloud(words = mid_ratings_adj, 
         min.freq = 5,  # Minimum frequency of words
         scale = c(3, 1),  # Size range for words
         colors = brewer.pal(8, "Greens"))
```

## High Ratings

```{r, echo=FALSE, warning=FALSE}
wordcloud(words = high_ratings_adj, 
         min.freq = 5,  # Minimum frequency of words
         scale = c(3, 1),  # Size range for words
         colors = brewer.pal(8, "Oranges")) 





```


